### 2019-03-19 papers/journal/encoding.tex
results update

\subsection{Encoding for $\fqbf$ search problem}
\label{enc:univ-cond}
%
Recall that the specification for universal condition~\ref{sec:property} requires quantifier alternation. 
%
Most SAT solvers can not efficiently handle the quantifier in the formulas. 
% 
Although, it is possible to encode the universal condition as a SAT or SMT problem.
%
There is always a danger of a blow-up in the formula size, making it harder for the SAT solver to handle. 
%Which may blow up the formula size for the solver to solve.
% 
As an experiment, we have implemented a direct SMT version of the universal problem extending the current $\fsmt$ search encodings.
%
The basic idea is to conjunct the formula for each combination value of the quantified variable. 
%
%
\input{satqbf-table}
%
The table~\ref{tab:satqbf-graph}, shows the search results of this encoding for the universal condition with 5 nodes and 3-connected graphs. 
%
The SMT extended version was not able to scale it to the desired results and either timed-out (T/O) or ran out of memory (M/O).
%
This can be due to the fact that directly translating a quantified formula into a quantifier-free  by introducing a vector of variables for each boolean possibility will blow up the size of the formula and may not be solvable by a solver.
%

@@

\paragraph{$k$-connected property}
%
$k$-connectedness expresses robustness against failure of few edges.
%
Let us use $d_{i,j,q}$ to indicate $q$th edge between $i$ and $j$ is failed
and $r'_{i,j}$ to indicate if there is a path from $i$ to $j$ in
the modified VTS.
%
% To check whether $k$-connected is a
% necessary condition, we remove (drop) $k-1$ edges from the graph and
% if it disconnects the graph, and we get an assignment.
% %
% We have a graph that is not $k$-connected.
%
In the following, $\texttt{Fail}(d,k)$ encodes that only
existing edges can be failed and exactly $k-1$ edges are failed.
%
$\texttt{FReach}(d,r')$ defines reachability in the modified VTS.
%
We use a new variable $r'_{i,j,p}$ to encode reachability from
$i$ to $j$ in at most $p$ steps.
%
$\texttt{Connected}(r')$ says that all nodes are reachable from any
other node.
\begin{align*}
\texttt{Fail}(d,k) = & 
\bigwedge\limits_{i,j,q} d_{i,j,q} \limplies e_{i,j,q}  \land 
\sum_{i,j,q} d_{i,j,q} = k-1\\
% \texttt{ReachAbove}(d,r') = &
% \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}_{i,j}\\
\texttt{FReach}(d,r') = &\hspace{-1ex}
\bigwedge\limits_{i,j,p}  \hspace{-1ex}r^{\prime}_{i,j,p} \hspace{-1ex}\limplies\hspace{-1ex} [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \hspace{-1pt}\lor \hspace{-2pt} (\bigvee_{\mathclap{i' \neq i}}  r^{\prime}_{i',j,p-1} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ]\\
\texttt{Connected}(r') = & \Land\limits_{i,j} (r^{\prime}_{i,j,\nu} \lor r^{\prime}_{j,i,\nu})
\end{align*}
%We will be synthesizing $k$-connected graphs.
%
We define $\texttt{Connected}(k)$ that says for all possible valid failures
the graph remains reachable. 
\begin{align*}
\texttt{Connected}(k) = & \forall d.\;
(\texttt{Fail}(d,k) \limplies \exists r'.\;\texttt{FReach}(d,r')
\land \texttt{Connected}(r'))
% \\
% \texttt{Disconnected}(k) = & \exists d.\;
%         (\texttt{Drop}(d,k) \land \exists r'.\;\texttt{ReachAbove}(d,r')
%                               \land \lnot \texttt{Connected}(r'))
\end{align*}
Since $d$ variables in $\texttt{Connected}(k)$ are universally
quantified, $\texttt{Connected}(k)$ introduces quantifier alternations.
%
%Therefore, synthesis against this property will require QBF reasoning.
%%
%We may make the formula quantifier free  by considering all possible failures
%separately and introducing a vector of reachability variables for each
%failure.
%%
%However, this will blow up the size of the formula and may not be
%solvable by a SAT solver.
%

>>>>

\subsection{Encoding for $\fqbf$ search problem}
\label{enc:univ-cond}
%
Recall that the specification for universal condition~\ref{sec:property} requires quantifier alternation. 
%
Most SAT solvers can not efficiently handle the quantifier in the formulas. 
% 
Although, it is possible to encode the universal condition as a SAT or SMT problem.
%
There is always a danger of a blow-up in the formula size, making it harder for the SAT solver to handle. 
%Which may blow up the formula size for the solver to solve.
% 
As an experiment, we have implemented a direct SMT version of the universal problem extending the current $\fsmt$ search encodings.
%
The basic idea is to conjunct the formula for each combination value of the quantified variable. 
%
%
\input{satqbf-table}
%
\todo{Fix the table; the entries of constraint is incorrect}The table~\ref{tab:satqbf-graph}, shows the search results of this encoding for the universal condition with 4 nodes and 3-connected graphs. 
%
The SMT extended version was not able to scale it to the desired results and either timed-out (T/O) or ran out of memory (M/O).
%
This can be due to the fact that directly translating a quantified formula into a quantifier-free  by introducing a vector of variables for each boolean possibility will blow up the size of the formula and may not be solvable by a solver.
%

@@

\paragraph{$k$-connected property}
%
$k$-connectedness expresses robustness against failure of few edges.
%
Let us use $d_{i,j,q}$ to indicate $q$th edge between $i$ and $j$ is failed
and $r'_{i,j}$ to indicate if there is a path from $i$ to $j$ in
the modified VTS.
%
% To check whether $k$-connected is a
% necessary condition, we remove (drop) $k-1$ edges from the graph and
% if it disconnects the graph, and we get an assignment.
% %
% We have a graph that is not $k$-connected.
%
In the following, $\texttt{Fail}(d,k)$ encodes that only
existing edges can be failed and exactly $k-1$ edges are failed.
%
$\texttt{FReach}(d,r')$ defines reachability in the modified VTS.
%
We use a new variable $r'_{i,j,p}$ to encode reachability from
$i$ to $j$ in at most $p$ steps.
%
$\texttt{Connected}(r')$ says that all nodes are reachable from any
other node.
\begin{align*}
\texttt{Fail}(d,k) = & 
\bigwedge\limits_{i,j,q} d_{i,j,q} \limplies e_{i,j,q}  \land 
\sum_{i,j,q} d_{i,j,q} = k-1\\
% \texttt{ReachAbove}(d,r') = &
% \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}_{i,j}\\
\texttt{FReach}(d,r') = &\hspace{-1ex}
\bigwedge\limits_{i,j,p}  \hspace{-1ex}r^{\prime}_{i,j,p} \hspace{-1ex}\limplies\hspace{-1ex} [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \hspace{-1pt}\lor \hspace{-2pt} (\bigvee_{\mathclap{i' \neq i}}  r^{\prime}_{i',j,p-1} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ]\\
\texttt{Connected}(r') = & \Land\limits_{i,j} (r^{\prime}_{i,j,\nu} \lor r^{\prime}_{j,i,\nu})
\end{align*}
%We will be synthesizing $k$-connected graphs.
%
We define $\texttt{Connected}(k)$ that says for all possible valid failures
the graph remains reachable. 
\begin{align*}
\texttt{Connected}(k) = & \forall d.\;
(\texttt{Fail}(d,k) \limplies \exists r'.\;\texttt{FReach}(d,r')
\land \texttt{Connected}(r'))
% \\
% \texttt{Disconnected}(k) = & \exists d.\;
%         (\texttt{Drop}(d,k) \land \exists r'.\;\texttt{ReachAbove}(d,r')
%                               \land \lnot \texttt{Connected}(r'))
\end{align*}
Since $d$ variables in $\texttt{Connected}(k)$ are universally
quantified, $\texttt{Connected}(k)$ introduces quantifier alternations.
%
%Therefore, synthesis against this property will require QBF reasoning.
%%
%We may make the formula quantifier free  by considering all possible failures
%separately and introducing a vector of reachability variables for each
%failure.
%%
%However, this will blow up the size of the formula and may not be
%solvable by a SAT solver.
%
%\begin{align*}
%  & \forall G \, \texttt{Connectivity(k)} \limplies  \exists
%                        f,p: \texttt{Stability} \, \land \, \texttt{Consistancy}  
%  \tag{U}\label{eq:univcond}
%\end{align*}
